### 2017-03-30 paper/evaluation.tex
done with subj section

We evaluated the characteristics of regression tests in open-source
development from a sample set of Java projects from \github{}.  We are
interested to evaluate non-trivial test suites on popular projects
that are in activity. We used the \github{}'s search
API~\cite{githubsearch} to fetch Java projects according to the
following criteria: (1) the primary language must be Java\footnote{In
case of projects in multiple languages, the \github{} API considers
the predominant language as the primary language.}; (2) the project
has at least 100 stars; (3) latest update on (or after) January 1st,
2016; (4) the \emph{readme} file contains the string \emph{mvn}.

@@

As of March 25th 2017, our search criteria returned \SubjectsGithub{}
subjects. Figure~\ref{fig:subjects} summarizes our sample set. From
the \SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
were not Maven projects (or did not have a \pomf{} in the root
directory) and \SubjectsGithubNotTestable{} were in an untestable
revision (\eg, missing dependencies or incompatible testing
environment). To ensure that our sample set is stable, we retested the
remaining subjects to eliminate flaky tests (total of
\SubjectsGithubFlaky{} subjects). Our final set consists in
\numSubjs{} testable subjects.

\vspace{-1ex}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.25\textwidth]{plots/subjs.pdf}
    \caption{\label{fig:subjects}\Fix{this is mocked data!}}
\end{figure}
\vspace{-2ex}

>>>>

We evaluated the characteristics of test suites in open-source
development from a sample set of Java projects from \github{}.  We are
interested to evaluate non-trivial test suites from popular projects
that are in activity. We used the \github{}'s search
API~\cite{githubsearch} to fetch Java projects according to the
following criteria: (1) the primary language must be Java\footnote{In
case of projects in multiple languages, the \github{} API considers
the predominant language as the primary language.}; (2) the project
has at least 100 stars; (3) latest update on (or after) January 1st,
2016; (4) the \emph{readme} file contains the string \emph{mvn}.

@@

As of March 25th 2017, our search criteria returned \SubjectsGithub{}
subjects. Figure~\ref{fig:subjects} summarizes our sample set. From
the \SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
were not Maven projects (or did not have a \pomf{} in the root
directory) and we were unable to execute the tests from
\SubjectsGithubNotTestable{} tests (\eg, missing dependencies or
incompatible testing environment). To ensure that our sample set is
stable, we retested the remaining subjects to eliminate flaky tests
(total of \SubjectsGithubFlaky{} subjects). Our final set consists in
\numSubjs{} testable subjects.

\vspace{-1ex}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.25\textwidth]{plots/subjs.pdf}
    \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular
    projects hosted on \github{}. From this initial sample, we ignored
    \SubjectsGithubNotMaven{} projects without Maven support,
    \SubjectsGithubNotTestable{} untestable projects, and
    \SubjectsGithubFlaky{} projects with flaky tests. We considered
    \numSubjs{} projects to conduct our study.}
\end{figure}
\vspace{-2ex}
